Black swans in ecological time series\\Black swans in population dynamics\\Heavy-tailed ecological time series\\Black swans in ecological dynamics

### 2014-10-09 anderson-etal-blackswan-timeseries.tex
Shrink space around equations
Add verbatim package
A whole lot of paper writing/editing

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,lmargin=2.54cm,rmargin=2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{ragged2e}
\usepackage{color}

@@

\usepackage[round]{natbib}
\bibliographystyle{apalike}
\bibpunct{(}{)}{;}{a}{}{;}

@@

\setlength\parskip{0.16in}
\setlength\parindent{0in}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{-6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{-8pt plus 2pt minus 2pt}

\begin{document}
\input{values} % R output

%\begin{spacing}{1.4}
%\doublespacing
\onehalfspacing

\maketitle
\thispagestyle{empty}

\input{ms}

\bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}
%\bibliography{/Users/seananderson/Dropbox/tex/jshort,refs}

\clearpage
\section{Tables}

\input{sparks.tex}

@@

\input{figs.tex}

\begin{centering}
\LARGE
Supporting material\\[1.5em]
\end{centering}

\input{supp}

\input{supp-figs}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,lmargin=2.54cm,rmargin=2.54cm}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{ragged2e}
\usepackage{color}
\usepackage{verbatim}
\usepackage[sectionbib]{chapterbib}

\usepackage{amsmath}
% \makeatletter
% \g@addto@macro\normalsize{%
%   \setlength\abovedisplayskip{-20pt}
%   \setlength\belowdisplayskip{0pt}
%   \setlength\abovedisplayshortskip{-20pt}
%   \setlength\belowdisplayshortskip{0pt}
% }
% \makeatother

@@

\usepackage[round,sectionbib]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}

@@

\setlength\parskip{0.16in}
\setlength\parindent{0in}
\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{-6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{0pt plus 4pt minus 2pt}{-8pt plus 2pt minus 2pt}

\begin{document}

\maketitle

\input{values} % R output

\emph{Authors are listed alphabetically (ABCD!) and open to reordering.}

\textsuperscript{1}Earth to ocean research group, department of biological sciences, Simon Fraser University, Burnaby BC, V5A 1S6, Canada

\textsuperscript{2}School of Aquatic and Fishery Sciences, University of Washington, Box 355020, Seattle, WA 98195, USA

\textsuperscript{3}School of Resource and Environmental Management, Simon Fraser University, Burnaby, BC, V5A 1S6, Canada

\textsuperscript{*}Corresponding author: Sean C. Anderson; Earth to Ocean Research Group, Department of Biological Sciences, Simon Fraser University, Burnaby BC, V5A 1S6; Phone: 1-778-782-3989; E-mail: sean\_anderson@sfu.ca

%\begin{spacing}{1.4}
\doublespacing
%\onehalfspacing

\thispagestyle{empty}

\linenumbers

\include{ms}

@@

\input{figs}

\include{supp}

\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}

\include{stat-table}

\include{supp-figs}

### 2014-10-09 supp-figs.tex
A whole lot of paper writing/editing

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.75\textwidth]{perc-prob-increase-with-n}
\caption{
Expected percent increase in the probability of detecting heavy tails, Pr($\nu < 10$), with an additional ten time steps of data.
These values are based on the curve shown in Fig.~\ref{fig:correlates}d, which is based on the coefficient in Fig.~\ref{fig:correlate-coefs}.
For example, we have about a 12\% increased probability of observing heavy tails in a time series that has 60 time steps vs.\ a time series with 50 time steps.
}
\label{fig:perc-inc-p}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.27\textwidth]{order-level-estimates.pdf}
\caption{
Taxonomic-order-level posterior estimates of probabilty that $\nu < 10$ from a beta regression multilevel model accounting for the effect of time-series length. Estimates are at the geometric mean of time series length across all the data (approximately 27 time steps). Colour shading refers to the taxonomic classes as indicated in Fig.~\ref{fig:nu-coefs} and Fig.~\ref{fig:correlates} (yellow for fishes, green for insects, purple for birds, and red for mammals). Short vertical line segments indicate median posterior estimates. Long dotted vertical line throughout the figure indicates the median expected Pr($\nu < 10$) from the prior distribution.
}
\label{fig:order-estimates}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.70\textwidth]{perc-prob-increase-with-n}
\caption{
Expected percent increase in the probability of detecting heavy tails, Pr($\nu < 10$), with an additional ten time steps of data.
These values are based on the curve shown in Fig.~\ref{fig:correlates}d, which is based on the coefficient in Fig.~\ref{fig:correlate-coefs}.
For example, we have about a 12\% increased probability of observing heavy tails in a time series that has 60 time steps vs.\ a time series with 50 time steps.
}
\label{fig:perc-inc-p}
\end{center}
\end{figure}
